Multi-level modeling with Openflexo/\FML

### 2021-09-27 3-introduction.tex

>>>>

\textcolor{red}{Our modeling approach is based on two levels. The meta level (\FML) provides the (linguistic) concepts that are used to define the model level (ontological). The ontological level is used to define the models and meta-models that are needed. \FML allows to define models as first class entities (which we call VirtualModel) and to link them together (by extension). In the \mpc case study, we exploit this possibility to:
\begin{itemize}
    \item Extend and adapt existing models, keeping the previous ones, to meet changing modeling needs,
    \item Align this hierarchy of models with the process of their evolution.
\end{itemize}
This methodological choice allows us to adapt the models and keep track of their evolution each time the needs evolve.}

\textcolor{red}{Contrary to a classical multi-level approach, in which the notion of multi-level is integrated in the meta-model and must therefore be respected, our approach allows to build multi-levels on demand, and with the appropriate form. As a limitation, without multilevel-specific operators/concepts, the "custom" construction must be done explicitly during the model development and evolution process.}

\textcolor{red}{Our answer to the challenge is therefore not an answer using a classical multilevel approach that would allow an efficiency comparison with another classical multilevel answer, but an approach that proposes another organization of multilevels through the translation of needs into levels over time and the possibility to build an evolving hierarchy of adapted models. This is made possible by (1) the reification of the notion of model and the possibility to interconnect them (specialization) and (2) the freedom of meta-modeling (low model conformity, flexible meta-modeling).}

### 2021-09-27 8-discussion.tex
removing trailing whitespace
Updates from Overleaf

  Due to the fact that our approach is level-agnostic, our solution could have had more
  or fewer levels depending on the variations of the use case. However, the number of levels is related
  to the problem, making the approach fixed.

@@

  Due to the level-agnostic aspect of our approach, we could insert a new
  level, for example. It would consist in creating new concepts we would link
  to other ones. Then, we would add any necessary constraints on those concepts
  and on the relationships linking them to the other existing concepts. This type 
  of change can be done without much effort. On the other hand, making changes 
  to the existing models could be difficult. For example, given a requirement, 
  an instance cannot be changed into a concept easily. This case could occur if 
  the challenge had refined the specification by requiring specific design tasks. 
  In this context, we would have to transform the \inst{Design Task} instance into a concept 
  whose instances could have been "using agile methodology".

>>>>

  Due to the fact that our approach is level-agnostic, our solution could have had more
  or fewer levels depending on the variations of the use case. However, the number of levels is related
  to the problem, making the approach fixed.\textcolor{red}{AB: Fixed?}

@@

  Due to the level-agnostic aspect of our approach, we could insert a new
  level, for example. It would consist in creating new concepts we would link
  to other ones. Then, we would add any necessary constraints on those concepts
  and on the relationships linking them to the other existing concepts. This type
  of change can be done without much effort. On the other hand, making changes
  to the existing models could be difficult. For example, given a requirement,
  an instance cannot be changed into a concept easily. This case could occur if
  the challenge had refined the specification by requiring specific design tasks.
  In this context, we would have to transform the \inst{Design Task} instance into a concept
  whose instances could have been "using agile methodology"
